RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-18 paper.tex
cloud-friendly pargraphs

\begin{figure}
\includegraphics[width=\linewidth]{fig/system/system.pdf}
\caption{\label{fig:system}A diagram of RCloud's architecture}
\end{figure}

Design for cloud-friendly? This goes back to the point in the
introduction about playing nice with the rest of the ecosystem.

>>>>

\begin{figure}
\includegraphics[width=\linewidth]{fig/system/system.pdf}
\caption{\label{fig:system}A diagram of RCloud's architecture. Dashed
  lines represent features which not yet implemented.}
\end{figure}

The internal computing infrastructure of organizations has changed
radically in the last fifteen years or so. Much of the move toward the
``cloud'' brought with it an ecosystem of processes distributed over a
network (many times virtually defined) that communicate over a
high-level protocol of some sort. Messages are typically exchanged
over HTTP. HTTP is attractive because web browsers and servers are
ubiquituous and available in essentially all pieces hardware today,
from tiny sensors in sensor networks to handheld devices to laptops to
rack-mounted servers.

As a result, in our view HTTP has become the lingua franca of IPC in
an intranet. One of the design goals for RCloud was to provide an
attractive environment for creators of data-analysis scripts, but at
the same time to create a system that behaves as a first-class citizen
in the ecosystem of computer services and networks with an
organization.

%% Design for cloud-friendly? This goes back to the point in the
%% introduction about playing nice with the rest of the ecosystem.
